Overview

### 2019-03-16 notebooks/general_info.Rmd
breakdown by package functionality added, will have numbers tomorrow. also, did primitive classes

>>>>

Now, how about if we take all of R's base classes (i.e., those which occur naturally in R) and lump them all into a "primitive" class.
What sort of class-based polymorphism do we see, now?

```{r}
los_primitive_class <- lapply(los, function(lof) {lapply(lof, class_to_primitive_df)})
```

```{r}
total_mono_clas_prim <- apply_count_to_lopkg_c(los_primitive_class, args_count_all_mono_class)
total_mono_clas_functions_prim <- apply_count_to_lopkg_c(los_primitive_class, fun_count_all_mono_class)
```

Let's get the top poly class now.
```{r}
poly_class_args_prim <- reduce_extracted_lopkgs_to_one(apply_extract_to_lopkg(los_primitive_class, extract_poly_class_args))
poly_class_args_prim <- poly_class_args_prim[order(-poly_class_args_prim$count),] # sort by count
poly_class_args_prim$perc <- round(poly_class_args_prim$count/sum(poly_class_args_prim$count) * 100, 2)
```

```{r}
format_df_for_print(poly_class_args_prim[1:20,])
```

The low percentage numbers suggest that no one user-defined pattern contributes too much to the class-based polymorphism.
